sem

### 2023-01-31 scripts/workshop/sem.Rmd
troubleshooting error
add more notes

Make lagged data
```{r}
prev_cc <- comm_data

@@

@@

histograms
```{r}
comm_data %>% ggplot(.,aes(x=MeanWaterTempPredC)) + geom_histogram()
comm_data %>% ggplot(.,aes(x=size)) + geom_histogram()
comm_data %>% ggplot(.,aes(x=log10(size))) + geom_histogram()
comm_data %>% ggplot(.,aes(x=cc)) + geom_histogram()
comm_data %>% ggplot(.,aes(x=log(cc))) + geom_histogram()
comm_data %>% ggplot(.,aes(x=Prevalence)) + geom_histogram()
comm_data %>% ggplot(.,aes(x=log10(Prevalence+1))) + geom_histogram()

```
plots
```{r}
comm_data %>% ggplot(.,aes(x=MeanWaterTempPredC, y = cc)) + geom_point() + geom_smooth()
comm_data %>% ggplot(.,aes(x=MeanWaterTempPredC, y = log10(size))) + geom_point() + geom_smooth()
comm_data %>% ggplot(.,aes(x=MeanWaterTempPredC, y = Prevalence)) + geom_point() + geom_smooth()
comm_data %>% ggplot(.,aes(x=log10(cc), y = Prevalence)) + geom_point() + geom_smooth(method = "lm")
comm_data %>% ggplot(.,aes(x=log10(size), y = Prevalence)) + geom_point() + geom_smooth(method = "lm")
```

@@

@@

Lefcheck example

>>>>

Make lagged data - I'll use this later to compare results using lagged and not lagged data
```{r}
prev_cc <- comm_data

@@

This is just a way to visualize the SEM

@@

Just some histograms to check the distributions of the data

```{r}
comm_data %>% ggplot(.,aes(x=MeanWaterTempPredC)) + geom_histogram()
comm_data %>% ggplot(.,aes(x=size)) + geom_histogram()
comm_data %>% ggplot(.,aes(x=log10(size))) + geom_histogram()
comm_data %>% ggplot(.,aes(x=cc)) + geom_histogram()
comm_data %>% ggplot(.,aes(x=log(cc))) + geom_histogram()
comm_data %>% ggplot(.,aes(x=Prevalence)) + geom_histogram()
comm_data %>% ggplot(.,aes(x=log10(Prevalence+1))) + geom_histogram()

And some basic plots

```{r}
comm_data %>% ggplot(.,aes(x=MeanWaterTempPredC, y = cc)) + geom_point() + geom_smooth()
comm_data %>% ggplot(.,aes(x=MeanWaterTempPredC, y = log10(size))) + geom_point() + geom_smooth()
comm_data %>% ggplot(.,aes(x=MeanWaterTempPredC, y = Prevalence)) + geom_point() + geom_smooth()
comm_data %>% ggplot(.,aes(x=log10(cc), y = Prevalence)) + geom_point() + geom_smooth(method = "lm")
comm_data %>% ggplot(.,aes(x=log10(size), y = Prevalence)) + geom_point() + geom_smooth(method = "lm")
```

@@

#fix error
#sem <- psem(cc_temp, size_temp, prev_cc)
#sem_1 <- psem(cc_temp, size_temp, prev_temp_cc)
```

@@

Lefcheck example
This is example data and code that I got from Lefcheck's tutorial
https://cran.r-project.org/web/packages/piecewiseSEM/vignettes/piecewiseSEM.html#worked-example
